Exploratory analysis using Copykat

### 2024-11-07 analyses/cell-type-wilms-tumor-06/notebook/07_combined_annotation_across_samples_exploration.Rmd

metadata <- read.table(sample_metadata_file, sep = "\t", header = TRUE)

# Create a data frames of all annotations
cell_type_df <- unique(metadata$scpca_sample_id) |>
  purrr::map(
    # For each sample_id, do the following:
    \(sample_id) {
      # This sample was run with "none" for reference
      if (sample_id == "SCPCS000190") {
        reference <- "none"
      } else {
        reference <- "both"
      }
      input_file <- file.path(
        result_dir,
        sample_id,
        glue::glue("06_infercnv_HMM-i3_{sample_id}_reference-{reference}.rds")
      )

>>>>

metadata <- read.table(sample_metadata_file, sep = "\t", header = TRUE)
sample_ids <- metadata |>
  dplyr::filter(seq_unit != "spot") |>
  dplyr::pull(scpca_sample_id) |>
  unique()

# Create a data frames of all annotations
cell_type_df <- sample_ids |>
  purrr::map(
    # For each sample_id, do the following:
    \(sample_id) {
      # This sample was run with "none" for reference
      if (sample_id == "SCPCS000190") {
        reference <- "none"
      } else {
        reference <- "both"
      }
      input_file <- file.path(
        result_dir,
        sample_id,
        glue::glue("06_infercnv_HMM-i3_{sample_id}_reference-{reference}.rds")
      )

### 2024-11-07 analyses/cell-type-wilms-tumor-14/exploratory_analysis/03_cnv/03_copykat_SCPCL000850.Rmd

## Input files
# load pre-processed sample objs & anchor transfer results
obj <- SeuratObject::LoadSeuratRds( file.path(path_anal,"scratch","00_preprocessing_rds",paste0(library_id,".rdsSeurat")) )
level <- "compartment"
predictions <- read.csv( file.path(path_anal, "results", "01_anchor_transfer_seurat", paste0(library_id, "_", level,".csv")) ) 
obj <- AddMetaData(object = obj, metadata = predictions)
copykat_result <- readr::read_rds( file = file.path(library_out_dir, paste0(library_id, "_copykat_resultobj.rds")) )
copykat_result_noref <- readr::read_rds( file = file.path(library_out_dir, paste0(library_id, "_noref_copykat_resultobj.rds")) )

>>>>

## Input files
# load pre-processed sample objs & anchor transfer results
obj <- SeuratObject::LoadSeuratRds( file.path(path_anal,"scratch","00_preprocessing_rds",paste0(library_id,".rdsSeurat")) )
level <- "compartment"
predictions <- read.csv( file.path(path_anal, "results", "01_anchor_transfer_seurat", "RNA", paste0(library_id, "_", level,".csv")) ) 
obj <- AddMetaData(object = obj, metadata = predictions)
copykat_result <- readr::read_rds( file = file.path(library_out_dir, paste0(library_id, "_copykat_resultobj.rds")) )
copykat_result_noref <- readr::read_rds( file = file.path(library_out_dir, paste0(library_id, "_noref_copykat_resultobj.rds")) )
